Supplement for Open-Source machine learning BANTER acoustic classification of a cryptic echolocating species

### 2023-08-21 epacific/beakerBanter_epacific.Rmd
manuscript update
Updated Manuscript

```{r, banter export, eval=freshRun}
banter_data <- export_banter(data_ch1only, dropSpecies = c('BW', 'possBW'), 
                         dropVars = c('All_ici', 'Click_Detector_3_ici', 'sea_floor_depth_mean', 'sst_mean', 'productivity_mean', 'chlorophyll_mean',  'magnitude_gradient_mean'), training=TRUE)
saveRDS(banter_data, file='epacific_banter_data.rds')

banter_data_ici <- export_banter(data_ch1only, dropSpecies = c("BW", "possBW"), dropVars = c('sea_floor_depth_mean', 'sst_mean', 'productivity_mean', 'chlorophyll_mean',  'magnitude_gradient_mean'),training=TRUE)
saveRDS(banter_data_ici, file='epacific_banter_data_ici.rds')

banter_data_env <- export_banter(data_ch1only, dropSpecies = c("BW", "possBW"), training=TRUE)
saveRDS(banter_data_env, file='epacific_banter_data_env.rds')

@@

```{r, banter ec detector model, eval=freshRun}
banter_model_ec <- initBanterModel(banter_data$events)
banter_model_ec <- addBanterDetector(banter_model_ec, banter_data$detectors, ntree=1e4, sampsize=3, importance = TRUE)

@@

```{r,save banter ec model, eval=freshRun}
saveRDS(banter_model_ec, 'epacific_banter_model_ec_t1e4s3_t1e4s4.rds')
```

@@

```{r, read banter model, include=FALSE, eval=!freshRun}
banter_model_ec <- readRDS('epacific_banter_model_ec_t1e4s3_t1e4s4.rds')
banter_model_ici <- readRDS('epacific_banter_model_ici_t1e4s3_t1e4s4.rds')
banter_model_env <- readRDS('epacific_banter_model_env_t1e4s1_t1e4s5.rds')
```

@@

```{r, importance heat map, include=TRUE, results=FALSE}
png(('../manuscript/manuscript_files/epacific_ec_importance.png'), width = 30, height = 25, units = 'cm',  res = 300)
plotImportance(banter_model_ec_RF, plot.type="heatmap")
dev.off()
ec_epacific_importance <- plotImportance(banter_model_ec_RF, plot.type="heatmap")

png(('../manuscript/manuscript_files/epacific_ici_importance.png'), width = 30, height = 25, units = 'cm',  res = 300)
plotImportance(banter_model_ici_RF, plot.type="heatmap")
dev.off()
ici_epacific_importance <- plotImportance(banter_model_ici_RF, plot.type="heatmap")

png(('../manuscript/manuscript_files/epacific_env_importance.png'), width = 30, height = 25, units = 'cm',  res = 300)
plotImportance(banter_model_env_RF, plot.type="heatmap")
dev.off()
env_epacific_importance <- plotImportance(banter_model_env_RF, plot.type="heatmap")
```

@@

```{r, Publication Figures, include=TRUE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_env_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_env_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_env_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_env_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

>>>>

```{r, banter export, eval=freshRun}
banter_data <- export_banter(data_ch1only, dropSpecies = c('BW', 'possBW'), 
                         dropVars = c('All_ici', 'Click_Detector_3_ici', 'sea_floor_depth_mean', 'sst_mean', 'productivity_mean', 'chlorophyll_mean',  'magnitude_gradient_mean', 'Latitude', 'Longitude', 'gpsUncertainty'), training=TRUE)
saveRDS(banter_data, file='epacific_banter_data.rds')

banter_data_ici <- export_banter(data_ch1only, dropSpecies = c("BW", "possBW"), dropVars = c('sea_floor_depth_mean', 'sst_mean', 'productivity_mean', 'chlorophyll_mean',  'magnitude_gradient_mean','Latitude', 'Longitude', 'gpsUncertainty'),training=TRUE)
saveRDS(banter_data_ici, file='epacific_banter_data_ici.rds')

banter_data_env <- export_banter(data_ch1only, dropSpecies = c("BW", "possBW"), dropVars = c('Latitude', 'Longitude', 'gpsUncertainty'), training=TRUE)
saveRDS(banter_data_env, file='epacific_banter_data_env.rds')

@@

```{r, banter ec detector model, eval=freshRun}
banter_model_ec <- initBanterModel(banter_data$events)
banter_model_ec <- addBanterDetector(banter_model_ec, banter_data$detectors, ntree=1e4, sampsize=4, importance = TRUE)

@@

```{r,save banter ec model, eval=freshRun}
saveRDS(banter_model_ec, 'epacific_banter_model_ec_t1e4s4_t1e4s4.rds')
```

@@

```{r, read banter model, include=FALSE, eval=!freshRun}
banter_model_ec <- readRDS('epacific_banter_model_ec_t1e4s4_t1e4s4.rds')
banter_model_ici <- readRDS('epacific_banter_model_ici_t1e4s3_t1e4s4.rds')
banter_model_env <- readRDS('epacific_banter_model_env_t1e4s1_t1e4s5.rds')
```

@@

```{r, importance heat map, include=TRUE, results=FALSE}
png(('../manuscript/manuscript_files/epacific_ec_importance.png'), width = 30, height = 25, units = 'cm',  res = 300)
plotImportance(banter_model_ec_RF, plot.type="heatmap", n=10)
dev.off()
ec_epacific_importance <- plotImportance(banter_model_ec_RF, plot.type="heatmap", n=10)

png(('../manuscript/manuscript_files/epacific_ici_importance.png'), width = 30, height = 25, units = 'cm',  res = 300)
plotImportance(banter_model_ici_RF, plot.type="heatmap", n=10)
dev.off()
ici_epacific_importance <- plotImportance(banter_model_ici_RF, plot.type="heatmap", n=10)

png(('../manuscript/manuscript_files/epacific_env_importance.png'), width = 30, height = 25, units = 'cm',  res = 300)
plotImportance(banter_model_env_RF, plot.type="heatmap", n=10)
dev.off()
env_epacific_importance <- plotImportance(banter_model_env_RF, plot.type="heatmap", n=10)
```

@@

```{r, Publication Figures, include=TRUE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=300, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=300, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=300, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=300, color = "black")

@@

confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=300, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=300, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=300, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=300, color = "black")

@@

confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_env_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=300, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_env_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=300, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_env_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=300, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_env_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=300, color = "black")

### 2023-08-21 hawaii/beakerBanter_hawaii.Rmd
manuscript update
Updated Manuscript

Create Figure for Publication
```{r, Publication Figure, include=TRUE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

>>>>

Create Figure for Publication
```{r, Publication Figure, include=TRUE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=300, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=300, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=300, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=300, color = "black")

@@

confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=300, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=300, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=300, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'hawaii_ici_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=300, color = "black")

### 2023-08-21 manuscript/Supplement.qmd
manuscript update
Updated Manuscript

## EC_ICI_ALT Model
Detector Model:  ntree=1e4, sampsize=5; 
Event Model: ntree=1e4, sampsize=5
```{r, NAtlantic EC_ICI_ALT Model Figure,  echo=FALSE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_alt_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_alt_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_alt_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_alt_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

# SAtlantic
## EC Model
Detector Model:  ntree=1e4, sampsize=2; 
Event Model: ntree=1e5, sampsize=1
```{r, SAtlantic EC Model Figure,  echo=FALSE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

## EC_ICI_ALT Model
Detector Model:  ntree=1e4, sampsize=4; 
Event Model: ntree=1e5, sampsize=2
```{r, SAtlantic EC_ICI_ALT Model Figure,  echo=FALSE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

>>>>

## EC_ICI_ALT Model
Detector Model:  ntree=1e4, sampsize=5; 
Event Model: ntree=1e5, sampsize=5
```{r, NAtlantic EC_ICI_ALT Model Figure,  echo=FALSE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_alt_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_alt_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_alt_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'natlantic_alt_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

# SAtlantic
## EC Model
Detector Model:  ntree=1e4, sampsize=8; 
Event Model: ntree=1e5, sampsize=1
```{r, SAtlantic EC Model Figure,  echo=FALSE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

## EC_ICI_ALT Model
Detector Model:  ntree=1e4, sampsize=4; 
Event Model: ntree=1e5, sampsize=3
```{r, SAtlantic EC_ICI_ALT Model Figure,  echo=FALSE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

@@

## EC_ICI Model
Detector Model:  ntree=1e4, sampsize=3; 
Event Model: ntree=1e4, sampsize=4

```{r, EPacific EC ICI Model Figure,  echo=FALSE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'epacific_ici_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

epacific_ici_Figure <-image_append(c(prox, heat, vote))
epacific_ici_Figure<- image_append(c(confuse, epacific_ici_Figure), stack=TRUE)
print(epacific_ici_Figure, info=FALSE)
```
